\Huge{{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}}

### 2021-05-09 paper/paper.tex
Updated title pag

%%%%%%%%%%%%%%%%%%
% TITLE
%%%%%%%%%%%%%%%%%%
\title{\Huge{\textbf{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}}}
\date{May 2021}
\author{
\Large{Adam David Bruce} \\ \texttt{\href{mailto:a.bruce3@newcastle.ac.uk}{a.bruce3@newcastle.ac.uk}}}
\begin{document}
\maketitle

@@

\iffalse
A summary of the tests used is provided below.

\begin{table}[H]
\centering
\begin{tabular}{ |c|c|c|c|c| } 
\hline
Name\\
\hline
Get block hash (invalid, buffer is null)\\
Get block hash (invalid, buffer too small)\\
Get block hash (invalid, block is null)\\
Get block hash (valid)\\
Get hash string (invalid, hash is null)\\
Get hash string (invalid, buffer too small)\\
Get hash string (invalid, buffer is null)\\
Get hash string (valid)\\
Initialise network stack (valid)\\
Clean up network stack (valid)\\
Send and receive message (valid)\\
Get Local IP Address (valid)\\
Load hosts from file (valid)\\
Add host (valid)\\
Initialise socket API (valid)\\
Clean up socket API (valid)\\
Create socket (valid)\\
Bind sending socket (valid)\\
Bind receiving socket (valid)\\
Bind socket (invalid, null socket)\\
Bind socket (invalid, port already in use)\\
Send and receive over socket (valid)\\
\hline
\end{tabular}
\caption{Unit Tests}
\label{tab:unittests}
\end{table}
\fi

@@

\item \textbf{Message Efficiency} - Currently the protocol is hugely inefficient in regards to the number of messages transmitted across the network. The use of hops and the fact that each host relays any message it receives to all of its known hosts creates an exponential amount of messages on the network, which means that should the number of hosts reach a high enough level, the network essentially becomes on big Distributed Denial-of-Service (DDOS) attack, potentially causing devices to spend too much time processing messages instead of processing genuine traffic. The efficiency of messages could be vastly improved by integrating a more effective mechanism for providing redundancy.

@@

%\fi

>>>>

%%%%%%%%%%%%%%%%%%
% TITLE
%%%%%%%%%%%%%%%%%%
\iffalse
\title{\Huge{{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}}}
\date{May 2021}
\author{
\Large{Adam David Bruce} \\ \texttt{\href{mailto:a.bruce3@newcastle.ac.uk}{a.bruce3@newcastle.ac.uk}}}
\begin{document}
\maketitle
\fi

\begin{document}

\begin{center}
\thispagestyle{empty}
\Huge{{Using Blockchain to Create a Decentralised Security Model for Distributed Systems}} \\
\vspace{1.0cm}
\LARGE{Adam David Bruce} \\ 
\vspace{1.0cm}
\LARGE{May 2021} \\
\vspace{13.0cm}
\LARGE{Computer Science (Security and Resilience)} \\
\vspace{1.0cm}
\LARGE{Supervisor: Dr John Mace} \\
\vspace{1.0cm}
\LARGE{{Word count: 14,993}}
\end{center}

\newpage
\section*{Declaration}
\say{I declare that this dissertation represents my own work except where otherwise stated.}

@@

A summary of the tests used is provided below.

\begin{table}[H]
\centering
\begin{tabular}{ |c|c|c|c|c| } 
\hline
Name\\
\hline
Get block hash (invalid, buffer is null)\\
Get block hash (invalid, buffer too small)\\
Get block hash (invalid, block is null)\\
Get block hash (valid)\\
Get hash string (invalid, hash is null)\\
Get hash string (invalid, buffer too small)\\
Get hash string (invalid, buffer is null)\\
Get hash string (valid)\\
Initialise network stack (valid)\\
Clean up network stack (valid)\\
Send and receive message (valid)\\
Get Local IP Address (valid)\\
Load hosts from file (valid)\\
Add host (valid)\\
Initialise socket API (valid)\\
Clean up socket API (valid)\\
Create socket (valid)\\
Bind sending socket (valid)\\
Bind receiving socket (valid)\\
Bind socket (invalid, null socket)\\
Bind socket (invalid, port already in use)\\
Send and receive over socket (valid)\\
\hline
\end{tabular}
\caption{Unit Tests}
\label{tab:unittests}
\end{table}

@@

\item \textbf{Message Efficiency} - Currently the protocol is hugely inefficient in regards to the number of messages transmitted across the network. The use of hops and the fact that each host relays any message it receives to all of its known hosts creates an exponential amount of messages on the network, which means that should the number of hosts reach a high enough level, the network essentially creates a Distributed Denial-of-Service (DDOS) attack, potentially causing devices to spend too much time processing messages instead of processing genuine traffic. The efficiency of messages could be vastly improved by integrating a more effective mechanism for providing redundancy.

@@
